Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-09-06 3dpas_intro.tex
small tweaks

Starting with the experience of the attendees of the Dynamic Distributed Data Programming Abstractions and Systems workshops (3DPAS), we have
assembled a set of D3 ``applications'' that we describe in this section.  
%We realize that we have overloaded the term ``application'' here.

@@

Against this backdrop, we eschew a formal classification of application types,
however, to facilitate understanding we categorize applications into two
categories: the first is that of {\em traditional applications}, where
% traditional is  applications are {\em traditional applications}, in that 
a program (or set of programs) is developed independently by a user or project to try to
answer a science question (or set of related questions). 
A single standalone computer program, a distributed application, or a
complex workflow could fall under the category of a {\em traditional
application}.  Applications in this paper that are in this category are: NGS (next generation
sequencing) Analytics (\S\ref{bioSilvia}), CMB (cosmic microwave background)
(\S\ref{astroJulian}), Fusion (\S\ref{fusionScott}), Industrial Incident
Notification and Response (\S\ref{Kees}), MODIS (moderate resolution imaging
spectroradiometer) Data Processing (\S\ref{modisKeith}), and Distributed Network
Intrusion Detection (\S\ref{detectionJon}).

Another group of applications are {\em infrastructural applications}.
Applications of this type are collaborative, in that they depend on a context
that is often agreed upon by a community, most often in terms of how data is
stored by the community and how it is accessed, as well as, more often than not,
a weak consensus on the infrastructure to be used.  This allows different
sub-applications (which themselves are full-fledged ``applications'', but with dependencies on the collaborative infrastructure) to focus on
different stages, such as generating data, or processing data.  Answering a
science question now may involve a set of applications that need to be run in
series, perhaps in different stages, that may be run by different groups that do
not frequently interact.  In this paper, examples of this type of application includes: ATLAS/WLCG (a
toroidal large hadron collider apparatus/worldwide large hadron collider
computing grid, \S\ref{WLCGSteve}), LSST (large synoptic survey telescope,
\S\ref{astroAdam}), SOA (service-oriented architecture) Astronomy
(\S\ref{astroSOAAdam}), Sensor Network Application (\S\ref{sensorSimon}),
Climate (\S\ref{climateDan}), Interactive Exploration of Environmental Data
(\S\ref{envJon}), and Power Grids (\S\ref{power}).

>>>>

Starting with the experience of the attendees of the Dynamic Distributed Data Programming Abstractions and Systems (3DPAS) workshops, we have
assembled a set of D3 ``applications'' that we describe in this section.  
%We realize that we have overloaded the term ``application'' here.

@@

Against this backdrop, we eschew a formal classification of application types,
however, to facilitate understanding we categorize applications into two
categories. The first is that of {\em traditional applications}, where
% traditional is  applications are {\em traditional applications}, in that 
a program (or set of programs) is developed independently by a user or project to try to
answer a science question (or set of related questions). 
A single standalone computer program, a distributed application, or a
complex workflow could fall under the category of a {\em traditional
application}.  Applications in this paper that are in this category are NGS (next generation
sequencing) Analytics (\S\ref{bioSilvia}), CMB (cosmic microwave background)
(\S\ref{astroJulian}), Fusion (\S\ref{fusionScott}), Industrial Incident
Notification and Response (\S\ref{Kees}), MODIS (moderate resolution imaging
spectroradiometer) Data Processing (\S\ref{modisKeith}), and Distributed Network
Intrusion Detection (\S\ref{detectionJon}).

Another group of applications are {\em infrastructural applications}.
Applications of this type are collaborative, in that they depend on a context
that is often agreed upon by a community, most often in terms of how data is
stored by the community and how it is accessed, as well as, more often than not,
a weak consensus on the infrastructure to be used.  This allows different
sub-applications (which themselves are full-fledged ``applications'', but with dependencies on the collaborative infrastructure) to focus on
different stages, such as generating data, or processing data.  Answering a
science question now may involve a set of applications that need to be run in
series, perhaps in different stages, that may be run by different groups that do
not frequently interact.  In this paper, examples of this type of application include
ATLAS/WLCG (a
toroidal large hadron collider apparatus/worldwide large hadron collider
computing grid, \S\ref{WLCGSteve}), LSST (large synoptic survey telescope,
\S\ref{astroAdam}), SOA (service-oriented architecture) Astronomy
(\S\ref{astroSOAAdam}), Sensor Network Application (\S\ref{sensorSimon}),
Climate (\S\ref{climateDan}), Interactive Exploration of Environmental Data
(\S\ref{envJon}), and Power Grids (\S\ref{power}).
